Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-03 article.tex
bookmark.

The atmospheric domain is described in \cref{fig:distributions}.
We tested domain division to various grids, from $10\times10 \times
20$ voxels, up to $50\times50 \times 100$. The corresponding voxels
had width, length and thickness of $5{\rm km}\times 5{\rm km} \times
0.5{\rm km}$ and $1{\rm km}\times 1{\rm km} \times 0.1{\rm km}$.  Each
ground-based camera has a hemispherical field of view, and low
resolution, $128 \rm{px} \times 128 \rm{px}$, as cloudless (yet hazy)
sky images are rather smooth.
\\

>>>>

The atmospheric domain is described in \cref{fig:distributions}.
We tested domain division to various grids, from $10\times10 \times
20$ voxels, up to $50\times50 \times 100$. The corresponding voxels
had width, length and thickness of $5{\rm km}\times 5{\rm km} \times
0.5{\rm km}$ and $1{\rm km}\times 1{\rm km} \times 0.1{\rm km}$.
\hl{We use finer vertical resolution to provide for higher variability
of air and aerosols distribution in the vertical dimension.} Each
ground-based camera has a hemispherical field of view, and low
resolution, $128 \rm{px} \times 128 \rm{px}$, as cloudless (yet hazy)
sky images are rather smooth.
\\

### 2013-10-03 opex2013_reply.tex
bookmark.

\item \textcolor{blue}{ ``The paper can be devided in two parts, one
    for computing single scattering, the other for multiple
    scattering. While the first part can be treated by a simple
    inverse transformation sampling as presented by the authors, the
    second part should have a different more complex inversion. For
    this reason I think that larger errors arise in multiple
    scattering. I feel the authors should dedicate some time to review
    this second part, that is more realistic."}

  {}

@@

  {There is no contradiction. The notation $F^{-1}$ refers to the
    inverse function of function $F$ and not to $\nicefrac{1}{F}$}

@@

  {Following the reviewer's comment, we have defined $\mu$ after
    Eq.~5, and revised the definition of the term ``voxel''. }

@@

  {}

@@

  {}

@@

  {}

>>>>

\item \textcolor{blue}{ ``The paper can be divided in two parts, one
    for computing single scattering, the other for multiple
    scattering. While the first part can be treated by a simple
    inverse transformation sampling as presented by the authors, the
    second part should have a different more complex inversion. For
    this reason I think that larger errors arise in multiple
    scattering. I feel the authors should dedicate some time to review
    this second part, that is more realistic."}

  {
    The reviewer raises a good point. Inverting the radiation transfer
    in the presence of multiple-scattering is the ``Holy Grail''
    of RT researchers. As far as we know there are no methods to
    solve this problem in the general case of non-homogeneous 3D
    atmosphere. Solutions are known only for a limited set of 
    situations.

    In this article we describe a novel data acquisition system
    and suggest a method to recover the 3D atmosphere based on
    the single-scattering approximation. Following the reviewer's
    suggestion we checked the limitations of the approximation
    by testing it in situations prone to high order of scatterings.
    Figures~5(b), 9(d) and 10(c) shows the results of applying
    out algorithm in a scene with dense aerosols distribution.
    Section~8 further discusses this experiment.
  }

@@

  {The notation $F^{-1}$ refers to the inverse function
   of function $F$ and not to $\nicefrac{1}{F}$.}

@@

  {We thank the reviewer for turning our attention to this.
   We replaced $\mu$ in Eq.~5 with its definition,
   $\cos \Phi^{\rm scatter})$. We revised the definition
   of the term ``voxel'', at the beginning of Sec.~4.}

@@

  {
    We now explain our vertical division of the atmosphere at the
    beginning of Sec.~5.
  }

@@

  {
    We appreciate the reviewer's comment. The issue raised by the
    reviewer is now discussed in Sec.~8. We also added Table~1 and
    Figs.~9 and 10, which show results of varying different properties
    of the aerosols and their distribution.
  }

@@

  {Following this comment, we tested  repeated the reconstruction
   simulations many times, each time varying the distance between
   cameras. The results are described in Sec.~8 and Fig.~8.}
